# Title: Machine Learning Course Project 

## Background inforamtion: 
Six participants wearing accelerometers on their belt, forearm, arm, and dumbell were asked to perform barbell lifts correctly and incorrectly in 5 different ways. Our goal is to predict the manner in which they did the exercise. Both training and testing data sets are from the website: http://groupware.les.inf.puc-rio.br/har 

## Load library
```{r echo=FALSE}
library(dplyr)
library(caret)
library(rattle)
library(rpart)
library(data.table)
```
## Data source 
```{r echo=TRUE}
url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
training <- fread(url)

url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
testing <- fread(url)
```

## Data cleaning. 
Remove variables with all missing values. Remove ID varaibles. 
```{r echo=TRUE}
isAnyMissing <- sapply(training, function (x) any(is.na(x) | x == ""))
keepVariable <- names(isAnyMissing)[!isAnyMissing]
keepVariable <- keepVariable[-c(1,2)]

```
### subset primary dataset with only related varialbes and outcome varialbe classe.
```{r echo=TRUE}
trainSet <- select_(training, .dots = keepVariable)
testSet <- select_(testing, .dots = keepVariable[-58])
```

## Create training and testing 
```{r echo=TRUE}
set.seed(1234)
inTrain = createDataPartition(trainSet$classe, p = 0.6)[[1]]
myTraining = trainSet[ inTrain,]
myTesting = trainSet[-inTrain,]
```
## Building models
### Method: random forest
```{r echo=TRUE}
set.seed(1234)
controlRF <- trainControl(method="cv", number=3, verboseIter=FALSE)
modelRF <- train(classe ~ ., data=myTraining, method="rf", trControl=controlRF)
modelRF$finalModel

predictRF <- predict(modelRF, newdata=myTesting)
confMatRF<- confusionMatrix(predictRF, myTesting$classe)
confMatRF
```
### Method: Decision Trees
```{r echo=TRUE}
set.seed(1234)
modelDT <- rpart(classe ~ ., data=myTraining, method="class")
fancyRpartPlot(modelDT)

predictDT <- predict(modelDT, newdata=myTesting, type="class")
confMatDT <- confusionMatrix(predictDT, myTesting$classe)
confMatDT
 
```                  
### Method: Generalized Boosted Model
```{r echo=TRUE}
set.seed(1234)
controlGBM <- trainControl(method = "repeatedcv", number = 5, repeats = 1)
modelGBM  <- train(classe ~ ., data=myTraining, method = "gbm",
                    trControl = controlGBM, verbose = FALSE)
modelGBM$finalModel

predictGBM <- predict(modelGBM, newdata=myTesting)
confMatGBM <- confusionMatrix(predictGBM, myTesting$classe)
confMatGBM
```
     
### Which model is more accurate
Comparing the three modesl used here: random forest, decision tree and generalized boosted model, we can see that random forest yield better accuracy. Thus we will use it to further predict our testing set. 
```{r echo=TRUE}
confMatRF$overall[1]
confMatDT$overall[1]
confMatGBM$overall[1]
```

## Making Test Set Predictions.
```{r echo=TRUE}
predictTEST <- predict(modelRF, newdata=testing)
predictTEST
```